Supplementary Material \\ Predicting Solid State Qubit Candidates

### 2021-12-11 supplementary.tex
Updates from Overleaf

\author{Oliver Lerstøl Hebnes}
\affiliation{Department of Physics and Center for Computing in Science Education, University of Oslo, N-0316 Oslo, Norway}

@@

Contents: \\ 
Supplementary methods --- information on machine learning approaches and the featurization process. \\ 
Supplementary results --- tables of resulting materials from the different approaches and models used.  \\ 
Supplementary references.

@@

\subsection*{Optimization of machine learning models}
Something important to add here??

\section*{Supplementary results}
Table~\ref{tab:03-probability-candidates}  displays the 66 predicted candidates that all models in the insightful approach agreed on with more than $75 \ \%$ probability.  All band gaps are taken from the Materials Project database as calculated using DFT and the PBE functional. Note that materials can appear several times  on  the  list  due  to  different  structures of the same composition. The  list  contains five  elementary (unary), 46  binary and  15 ternary compounds.

>>>>

\author{Oliver Lerst{\o}l Hebnes}
\affiliation{Department of Physics and Center for Computing in Science Education, University of Oslo, N-0316 Oslo, Norway}

@@

Contents: \\ 
Supplementary methods --- additional information on the featurization process and implementation of the machine learning models. \\ 
Supplementary results --- tables over the materials that were predicted by the machine learning models based on the training sets derived using the three different data mining approaches. \\ 
Supplementary references.

@@

\subsection*{Optimization of machine learning models}
Morten/Oliver please add details.

\section*{Supplementary results}
Table~\ref{tab:03-probability-candidates}  displays the 66 predicted candidates that all four machine learning models, using the data set derived in the intuitive approach, agreed on with more than $75 \ \%$ probability.  All band gaps are taken from the Materials Project database as calculated using DFT and the PBE functional. Note that materials can appear several times  on  the  list due  to  different  structures of the same composition. The  list  contains five elementary (unary), 46  binary and  15 ternary compounds.
